### 2019-01-25 intro.tex
ssr

\noindent
\underline{\textsf{Generalized NCFs:}}~
For some problems, we will also consider a more general form
of NCFs defined below.

@@

\noindent
\textbf{Note:} If a generalized NCF is not a constant, 
there is an assignment to its variables
such that the value of the function is 0,
and there is an assignment to its variables
such that the value of the function is 1.

>>>>

\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
\underline{\textsf{Generalized NCFs:}}~
For some problems, we will also consider a more general form
of NCFs defined below.

@@

\noindent
\textbf{Note:} If a generalized NCF is not a constant, 
there is an assignment to its variables
such that the value of the function is 0,
and there is an assignment to its variables
such that the value of the function is 1.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi

\subsection{Use of NCFs in Modeling Biological Systems}

The term \textbf{canalization} was first used by
Conrad Waddington (a British geneticist)
in 1942 \cite{Waddington-1942}
to express the ability of a species
to produce members with very similar observable features over a period
of time even when there are significant changes in the environment
during that period.
Since that time, the term ``canalization'' has been used to describe
the stability of a biological system with changes
in external conditions.
In 1969, Kauffman \cite{Kauffman-1969} introduced a Boolean network model
to explain the stability of gene regulatory networks.
Kauffman observed that the use of canalyzing Boolean
functions in the model captured many observed properties of
gene regulatory networks.
The subclass of NCFs was
introduced later by Kauffman et al. \cite{Kauffman-etal-2003} 
to facilitate a rigorous analysis of the Boolean network model
for gene regulatory networks.
